Solution-aware vs global ReLU selection: \\ partial MILP strikes back for DNN verification

### 2025-05-06 lipschitz/Lipschitz_a_proposition.tex
update the proposition

	For a number $\epsilon > 0$, $K_\epsilon$ is the smallest number such that for any $d\geq \epsilon$, any input $x,y$.
	\begin{align*}
	 |x-y| \leq d \implies |f(x)-f(y)| \leq dK_\epsilon 
	\end{align*}
\end{definition}

@@

		\item 	If we care about $\epsilon$ and compute the Lipschitz constant of $0.5 \epsilon$ and get $K$, then we can use Lipschizt constant $\leq K\frac{2+1}{2}$ for general larger $\epsilon$.
		\item 	Similarly, if we compute Lipschitz constant for any $\epsilon$ and get $K$, then we can use Lipschitz constant $K\frac{1+1}{1}$ for any larger $\epsilon$.
	\end{enumerate}
\end{corollary}

@@

\end{proposition}

>>>>

	For a number $\epsilon > 0$, $K_\epsilon$ is the smallest number such that for any $d\geq \epsilon$, any inputs $x,y$:\begin{align*}
	 |x-y| \leq d \implies |f(x)-f(y)| \leq dK_\epsilon 
	\end{align*}
\end{definition}

@@

		\item Therefore, for any inputs $x,y$ that $|x-y|\geq N\epsilon$ for an integer $N\geq 1$, \begin{align*}
			\dfrac{|f(x)-f(y)|}{|x-y|}\leq K_\epsilon\frac{N+1}{N}
		\end{align*}

		\item 	If for a number $\epsilon$, we get the value of $K_{0.5 \epsilon}$, then we will have a Lipschizt constant $\frac{2+1}{2}K_{0.5 \epsilon}$ working for $|x-y|\geq\epsilon$.

		\item 	Similarly, if for a number $\epsilon$, we get the value of $K_{\epsilon}$, then we will have a Lipschizt constant $\frac{1+1}{1}K_{\epsilon}$ working for $|x-y|\geq\epsilon$.
	\end{enumerate}
\end{corollary}

@@

\begin{proposition}
	Continue the definition. Suppose we have a number $K$ that for any $d$ in one of $\epsilon, 1.1\epsilon, 1.2\epsilon, \cdots, 1.9\epsilon$, we have $K_d\leq K$.

	Then, for any two inputs $x,y$,if $|x-y|\geq \epsilon$, then $\dfrac{|f(x)-f(y)|}{|x-y|}\leq 1.1 K$. 
\end{proposition}

\begin{proof}
	Let $x,y$ be any two inputs, we need to show that if $|x-y|\geq \epsilon$, then $\dfrac{|f(x)-f(y)|}{|x-y|}\leq 1.1 K$.

	If $|x-y| \geq 10\epsilon$, this is clear by above corollary part 2. So we need to consider $\epsilon\leq |x-y|< 10\epsilon$.

	For any inputs $x,y$ that $\epsilon\leq|x-y|< 10\epsilon$, there exists a sum $x_1+x_2+\cdots+x_n$ by numbers from (allowing repetitions) $\epsilon, 1.1\epsilon, 1.2\epsilon, \cdots, 1.9\epsilon$ such that \begin{align*}
	 \epsilon \leq x_1+x_2+\cdots+x_n -0.1\epsilon \leq |x-y| \leq x_1+x_2+\cdots+x_n
	\end{align*}

	By assumption, divide the line segment from $x$ to $y$ into pieces according to $x_1, x_2,\cdots,x_n$, then we will have $$|f(x)-f(y)|\leq Kx_1+Kx_2+\cdots+Kx_n.$$

	Hence,\begin{align*}
		\dfrac{|f(x)-f(y)|}{|x-y|} &\leq \dfrac{Kx_1+Kx_2+\cdots+Kx_n}{x_1+x_2+\cdots+x_n -0.1\epsilon}\\
		& = K\cdot( 1+  \dfrac{0.1\epsilon}{x_1+x_2+\cdots+x_n -0.1\epsilon})\\
		& \leq K\cdot( 1+  \dfrac{0.1\epsilon}{\epsilon})\\
		& \leq 1.1 K
	\end{align*}
